---
appendix: "Stage2_app001.Rmd"
---

# Sensitivity Analyses

```{r setup_a, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache = TRUE
)
```

```{r init_a, message=FALSE, warning=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

The R codes for the sensitivity analysis on the trial level were written by Erin M. Buchanan. 

## Load data and run models

The data for the sensitivity analysis shared the same exclusion criterion for the pre-registered mixed-effects models. The first step is to determine if there is a minimum number of trials required for stable results.

```{r Trial-count_a}
number_trials <- SP_V_correct %>% 
 group_by(Subject, Match) %>%
 summarize(count = n())
```

```{r model_a}
models <- list()

for (i in 3:12){

 subjects <- number_trials %>%
    filter(count >= i) %>%
    pull(Subject) %>% unique()

 temp_data <- SP_V_correct %>%
    filter(Subject %in% subjects)

 # match model in the paper
 models[[paste("fixed.three.model", i, sep = "_")]] <- lmer(response_time ~ Match + (1|Subject) + (1|Target) + (1|PSA_ID), 
            control = lmerControl(optimizer = "bobyqa",
                       optCtrl = list(maxfun = 1e6)), 
            data = temp_data)
}
```

## View the Results

```{r b-computation_a}
b_values <- 1:length(models)
p_values <- 1:length(models)
for (i in 1:length(models)){
 b_values[i] <- round(fixef(models[[i]])["MatchN"],2)
 p_values[i] <- apa_p(summary(models[[i]])$coefficients[2,5])
}

#b_values
#p_values
```

### b values

These values represent the *b* values found for each run of 3 up to 12 trials.

`r b_values`

### p values

These values represent the *p* values found for each run of 7 up to 12 trials.

`r paste(p_values, collapse = ", ")`

As we can see, the effect is generally negative until participants were required to have 7-12 correct trials. When participants accurately answer all 12 trials the effect is approximately 3 ms. Examination of the *p*-values indicates that no coefficients would have been considered significant. 

## Calculate the Sensitivity

Given we used all data points, the smallest detectable effect with our standard error and degrees of freedom would have been: 

```{r sense_a}
qt(p = .05/2, # two tailed 
  df = summary(models[[1]])$coefficients[2, 3],
  lower.tail = F) * summary(models[[1]])$coefficients[2, 2] 
```

